---
title: "FinalProject"
author: "Ximu Wang"
date: "2019/4/9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(pROC)
library(rsample)
library(xgboost)
```
## Import data
Import the data with real distance and duration
```{r}
train <- read.csv("train_final 2.csv")
test <- read.csv("test_final 2.csv")
head(train)
```
```{r}
summary(train)
```
delete the fare amount less than 0
```{r}
train <- train[train$fare_amount >= 0,]
```
remove missing data
```{r}
colSums(is.na(train))
```

Summary in picture
```{r}
library(ggplot2)

ggplot(data = train[train$fare_amount <= 80,], aes(x = fare_amount)) + 
  geom_histogram(col = "black", fill = "lightblue", bins = 100) +
  labs(title = "Histogram of fare_amount")
```

delete the data out of test set
```{r}
longitude.min <- min(min(test$pickup_longitude), min(test$dropoff_longitude))
longitude.min
longitude.max <- max(max(test$pickup_longitude), max(test$dropoff_longitude))
longitude.max
```
```{r}
latitude.min <- min(min(test$pickup_latitude), min(test$dropoff_latitude))
latitude.min
latitude.max <- max(max(test$pickup_latitude), max(test$dropoff_latitude))
latitude.max
```
present window on map
```{r}
#window
wind <- c(-74.5, -72.8, 40.60, 41.8)

fun.selectWind <- function(data, wind){
  return(data$pickup_longitude >= wind[1] & data$pickup_longitude <= wind[2] &
           data$pickup_latitude >= wind[3] & data$pickup_latitude <= wind[4] &
           data$dropoff_longitude >= wind[1] & data$dropoff_longitude <= wind[2] &
           data$dropoff_latitude >= wind[3] & data$dropoff_latitude <= wind[4])
}
```
refine the train set
```{r}
train <- train[fun.selectWind(train, wind),]
```

show the pick up location and drop off location on map
```{r}
library(ggmap)
register_google(key = "AIzaSyDLMjTSWFJozOFnS0bLIuu4RH5Eibjp0V4")
```

```{r}
map <- get_googlemap(center = c(-74, 40.75), maptype = "roadmap", zoom = 10)
mapplot.pickup <- ggmap(map) + labs(x = "longitude", y = "latitude") + 
  geom_point(aes(pickup_longitude,pickup_latitude),data=train,alpha=0.15, size=0.1, color="red")
mapplot.pickup
```

```{r}
mapplot.dropoff <- ggmap(map) + labs(x = "longitude", y="latitude")+
  geom_point(aes(dropoff_longitude,dropoff_latitude),data=train,alpha=0.15,size=0.1,color="red")
mapplot.dropoff
```

density map
```{r}
mapdensity.pickup <- ggmap(map) +
  stat_density2d(data = train, aes(x = pickup_longitude, y = pickup_latitude, fill = ..level.., alpha = ..level..),geom="polygon", bins=500,h=0.02)+
  scale_fill_gradient(low = "blue",high = "yellow")
mapdensity.pickup
```

```{r}
mapdensity.dropoff <- ggmap(map) +
  stat_density2d(data = train, aes(x = dropoff_longitude, y = dropoff_latitude, fill = ..level.., alpha = ..level..),geom="polygon", bins=500,h=0.02)+
  scale_fill_gradient(low = "blue",high = "yellow")
mapdensity.dropoff
```

scatter:distance~fare
```{r}
ggplot(data = train, aes(x = distance_meter, y = fare_amount)) + geom_point(size = 1,alpha=0.2,color="blue")
```
zoom
```{r}
ggplot(data = train[train$distance_meter <= 37500 & train$fare_amount<=100,], aes(x = distance_meter, y = fare_amount)) + geom_point(size = 1,alpha=0.2,color="blue")
```

Add the time information

```{r}
train$year <- as.factor(format(as.POSIXlt(train$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%Y'))
train$month <- as.factor(format(as.POSIXlt(train$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%m'))
train$day <- format(as.POSIXlt(train$pickup_datetime),format="%d")
```
```{r}
train$hour <- as.factor(format(as.POSIXlt(train$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%H'))
```

```{r}
test$year <- as.factor(format(as.POSIXlt(test$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%Y'))
test$month <- as.factor(format(as.POSIXlt(test$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%m'))
test$day <- format(as.POSIXlt(test$pickup_datetime),format="%d")
test$hour <- as.factor(format(as.POSIXlt(test$pickup_datetime,format='%Y-%m-%d %H:%M:%S'),format='%H'))
```

Add fare_per_distance
```{r}
train$fare_per_distance <- train$fare_amount/train$distance_meter * 1000
```

```{r}
library(rpivotTable)
rpivotTable(data = train, rows = "year", cols = "hour", vals = "fare_per_distance", aggregatorName = "Median", rendererName ="Line Chart", width="100%", height="400px")
```

use xgboost to predict
features: "passenger_count","distance_meter","duration_by_second","Year","Month","Hour"
          8,9,10,11,12,14
```{r}
change_test <- as.numeric(as.character(train$year))
change_test[1:5]
```

```{r}
train$year <- as.numeric(as.character(train$year))
train$month <- as.numeric(as.character(train$month))
train$hour <- as.numeric(as.character(train$hour))
test$year <- as.numeric(as.character(test$year))
test$month <- as.numeric(as.character(test$month))
test$hour <- as.numeric(as.character(test$hour))
```
```{r}
train.matrix <- xgb.DMatrix(data = as.matrix(train[,c(8,9,10,11,12,14)]), label = train$fare_amount)
test.matrix <- xgb.DMatrix(data = as.matrix(test[,c(7,8,9,10,11,13)]))

train_split <- initial_split(train, prop=0.9)
cvtrain <- training(train_split)
cvtest <- testing(train_split)
cvtrain.matrix <- xgb.DMatrix(data = as.matrix(cvtrain[,c(8,9,10,11,12,14)]), label = cvtrain$fare_amount)
cvtest.matrix <- xgb.DMatrix(data = as.matrix(cvtest[,c(8,9,10,11,12,14)]), label = cvtest$fare_amount)
```

```{r}
params <- list(booster = 'gbtree',
               objective = 'reg:linear',
               eta = 0.03,
               max_depth = 6,
               n_estimators = 500)
               subsample = 1,
               min_child_weight = 1.5,
               colsample_bytree = 0.2,
               scale_pos_weight = 3,
               gamma = 0.2,
               lambda = 300)
```
```{r}
xgb_cv <- xgb.cv(params = params, data = train.matrix, nfold = 4, print_every_n = 1, maximize = TRUE, nrounds = 1000, early_stopping_rounds = 75)
```
```{r}
watchlist <- list(val=cvtest.matrix)
```
```{r}
xgb.solve <- xgb.train(params = params, data = cvtrain.matrix, nrounds = 1000, watchlist = watchlist, early_stopping_rounds = 75)
```
```{r}
fare_amount <- predict(xgb.solve, test.matrix)
fare_amount
```

```{r}
test$fare_amount <- fare_amount
result <- test[, c("key", "fare_amount")]
head(result)
```
```{r}
write.csv(result,file = "result.csv", row.names = FALSE)
```

```{r}
lalala <- read.csv("train.csv", nrows = 1000)
head(lalala)
```


